\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-04-10 eg6-letters/NIM/EG6_RTPC_NIM.tex
NIM in progress...

{\bf \color{red} We should shortly discuss the choice of drift gas.}

@@

The RTPC electron collection system has 3200 readout pads. These elements are
located at the end of the amplification region, 69 mm from the central axis.

@@

Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment 
configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
width.  The shift between the rows allows to reduce aliasing. Each half of the 
RTPC has 40 rows and 40 columns of pads. The shaded region in figure~\ref{fig:PADs}
shows how pads are grouped to 16 channels pre-amplifiers.  A Time to Digital
Converter (TDC) with 114~ns samples is used to measure the time taken by
the electrons to drift from the ionization point to the readout board.  Signal
amplitude is is measured with an Analog-to-Digital-Converter (ADC) without
specific normalization.

Mention ALTRO chip and reference.

Sparcification.  3 consecutive ADC samples above a threshold of ?, and the three
samples before and after.

Missing items in description:

Detail the electronic setup: Andrea ? or other Italians?

The gas mixture choice: ???

Discuss HV setting: ???

\section{Calibration} \label{sec_calib}
Two quantities are recorded for each detected electron at the readout board, 
time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge 
preamps ???). The timing information provides trajectory determination 
resulting in momentum per unit charge measurement. Going from a collection of 
the TDCs to a momentum measurement requires good knowledge of the drift speed 
and paths followed by the electrons released in the gas. The recorded ADCs give 
the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, 
together with the momentum calculated from the trajectory, enables particle 
identification.

>>>>

{\bf \color{red} To be added:

Discuss the choice of drift gas

Discuss the self supporting mechanic of the GEMs.}

@@

@@

The RTPC electron collection system has 3200 readout pads. These elements are
located at the end of the amplification region, 69 mm from the central axis.
Figure \ref{fig:PADs} shows a schematic drawing of the size and 
configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
width.  The shift between the rows allows to reduce aliasing. Each half of the 
RTPC has 40 rows and 40 columns of pads. The shaded region in figure~\ref{fig:PADs}
shows how pads are grouped to 16 channels pre-amplifiers.  A Time to Digital
Converter (TDC) with 114~ns samples is used to measure the time taken by
the electrons to drift from the ionization point to the readout board.  Signal
amplitude is is measured with an Analog-to-Digital-Converter (ADC) without
specific normalization.

{\bf \color{red} 
Andrea:

- Mention ALTRO chip and reference.

- Sparcification method (3 consecutive ADC samples above a threshold of xxx ?, and three
samples before and after)

- Preamplifiers were from Bonus ?

- Basics of JLab fADC (is there a reference?)

- Other relevant information ?
}

\section{Calibration} \label{sec_calib}

{\bf \color{red} The use of the term TDC is improper and should be removed
everywhere. Replace by T.}

Two quantities are recorded at the readout board, 
time (T) and signal amplitude (ADC). The timing information is used to infer 
the origin of the charge and then the trajectory of the detected particle
resulting in momentum measurement. Going from a collection of 
times to a momentum measurement requires a good knowledge of the drift speed 
and drift paths followed by the electrons released in the gas. The recorded ADCs give 
the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, 
together with the momentum calculated from the trajectory, enables particle 
identification.

In this section we will detail the methods used to calibrate the drift speed,
drift paths and gains of the detector. Note that for drift speed and drift
path we use the symetry of the detector and ...
